%-------------------------
% Resume in Latex
% Author : Yapeng Shi
% Based off of: https://github.com/yapengshi
% This is yapeng's resume pdf version for homepage
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{https://yapengshi.github.io/}{\Large Yapeng Shi}} & Email : \href{mailto:shiyapeng66@163.com}{shiyapeng66@163.com}\\
%   \href{https://yapengshi.github.io/} & Mobile : +86-188-0462-0736 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape \href{https://yapengshi.github.io/}{Yapeng SHI}} \\ \vspace{1pt}
    \small +86-188-0462-0736 $|$
    \href{https://scholar.google.com/citations?user=00aEs2gAAAAJ&hl=en}{\underline{Scholar/yapeng}} $|$ \href{mailto:shiyapeng66@163.com}{\underline{shiyapeng66@163.com}} $|$ 
    \href{https://www.linkedin.com/in/YapengShi}{\underline{linkedin.com/yapengshi}} $|$
    \href{https://github.com/yapengshi}{\underline{github.com/yapengshi}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Harbin Institute of Technology}{Harbin, China}
      {Phd in Robotics, Advisor: Mantian Li}{September. 2015 -- Present}
    \resumeSubheading
      {Beijing Jiaotong University}{Beijing, China}
      {Bachelor of Mechanical Engineering}{September 2011 -- July 2015}
  \resumeSubHeadingListEnd
  
\vspace{-5mm}
\section{Research Interests}
 \begin{itemize}[leftmargin=0.2in, label={}]
\justifying \item I am generally interested in using Optimization, Whole-body Control and Machine Learning techniques to generate complex robot behaviors. My current research focuses on enabling legged robots to traverse complex environments, such as mammals, in a robust and agile manner.
\end{itemize}

\vspace{-7mm}
\section{Publications}
\begin{itemize}
	\setlength{\itemsep}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\parskip}{4pt}
\justifying	\item \textbf{Yapeng Shi}, Mantian Li, et al.: Force-controlled Compensation Scheme for PQ Valve-controlled Asymmetric Cylinder used on Hydraulic Quadruped Robots. \textbf{Journal of Bionic Engineering}, 2020.
	
\justifying	\item \textbf{Yapeng Shi}, Pengfeng Wang, Fusheng Zha, et al.: Mechanical design and force control algorithm for a robot leg with hydraulic series-elastic actuators. \textbf{International Journal of Advanced Robotic Systems}, 2020.
\justifying	\item \textbf{Yapeng Shi}, Pengfeng Wang, Mantian Li, et al.: Model predictive control for motion planning of quadrupedal locomotion. \textbf{IEEE International Conference on Advanced Robotics and Mechatronics}, 2019.
\justifying	\item Pengfeng Wang,\textbf{Yapeng Shi}, Fusheng Zha, et al.: An analytic solution for the force distribution based on Cartesian compliance models. \textbf{International Journal of Advanced Robotic Systems}, 2019.

\justifying	\item \textbf{Yapeng Shi}, Pengfei Wang, Xin Wang, et al.: Bio-inspired equilibrium point control scheme for quadrupedal locomotion. \textbf{IEEE Transactions on Cognitive and Developmental Systems}, 2018.

\justifying	\item ShuaiShuai Wang, \textbf{Yapeng Shi}, Wang Xin, et al.: State estimation for quadrupedal using linear inverted pendulum model. \textbf{IEEE International Conference on Advanced Robotics and Mechatronics}, 2017.

\justifying	\item \textbf{Yapeng Shi}, Changrong Cai, Wei Guo, et al.: Bio-inspired Control Framework for Legged Locomotion. \textbf{Dynamic Walking}, 2017.

\end{itemize}

\vspace{-7mm}
\section{Awards}
\begin{itemize}
	\setlength{\itemsep}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\parskip}{4pt}
\item Best Conference Paper Award Finalist, 2019.
\item HRG Best Advanced Robotics Paper Award, 2017.
\item Best Conference Paper Award Finalist, 2017.
\end{itemize}

%-----------EXPERIENCE-----------
\vspace{-7mm}
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {PhD visiting student at AIR Lab, University of Edinburgh}{September 2019 -- September,2020}
      {worked with Dr. Zhibin Li}{Edinburgh, UK}
%      Mainly focuse on Optimization-based Planning and Whole-body Force Control.
      \resumeItemListStart
        \resumeItem{Mainly focuse on Optimization-based Planning and Whole-body Force Control.}
%        \resumeItem{Developed a Whole-body controller for quadruped robot based on Centroidal Dynamics}
%        \resumeItem{Designed a 3D-printed little quadruped robot}
      \resumeItemListEnd
      
    \resumeSubheading
      {Research Assistant}{March 2017 -- October 2018}
      {Robotics Lab,  Shenzhen Academy of Aerospace Technology}{Shenzhen, China}
      \resumeItemListStart
        \resumeItem{Worked on Quadruped Locomotion.}
    \resumeItemListEnd

    \resumeSubheading
      {Intern}{June 2016 -- Febrary 2017}
      { Long-HIT Inc}{Shenzhen, China}
      \resumeItemListStart
        \resumeItem{Focused on Robot R\&D.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\vspace{-7mm}
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: C/C++, Python, \LaTeX} \\
     \textbf{Skill}{: ROS, Matlab, SolidWorks} 
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
